---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/elben10/resumr.svg?branch=master)](https://travis-ci.org/elben10/resumr)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/elben10/resumr?branch=master&svg=true)](https://ci.appveyor.com/project/elben10/resumr)[![CRAN status](http://www.r-pkg.org/badges/version/resumr)](https://cran.r-project.org/package=resumr)

## Installation

You can install `resumr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("elben10/resumr")
```

## `resumr`

`resumr` provides a Rmarkdown latex format for making a nice and formal resume (CV) in Rmarkdown. The goal of `resumr` is to make it very easy to create a formal cv using the markdown and code chunk syntax from Rmarkdown. The package does also provide a vignette that step by step shows how you create a resume using `resumr`.

`resumr` provides a single resume template at the moment, but the number of resume templates will be increased in the future.

## Creating a resume using `resumr`

There is basically two ways to create a resume using `resumr`. (1) Using Rstudio (2) Using plain R.

1) In Rstudio you can create a `resumr` resume by using the new file button in Rstudio and then choose `R Markdown...`. Choose `From Template`, and then choose `Academic Resume`. Finally, you just knit your document as you would with all other `.Rmd` documents. A more thorough description can be find in the readme file in the [`rticles` packages](https://github.com/rstudio/rticles/blob/master/README.md). 

1) It is possible to create a `resumr` draft using the `draft` function from the [`rmarkdown package`](http://rmarkdown.rstudio.com). To create a draft and compile it you will do the following: 
    1) `rmarkdown::draft("MyDraft.Rmd", template = "academic_cv", package = "resumr)`
       `rmarkdown::render("MyDraft.Rmd")`
       


